Julia for HPC: In Situ Data Analysis with Julia for Climate Simulations at Large Scale

### 2024-04-15 paper/paper.tex
Update paper.tex

Julia is a dynamically-typed programming language that is for general-purpose application development and provides many Python-like features (e.g., rich package support)~\cite{bezanson2012julia}. The first public Julia release was introduced in 2013 and it is designed to provide users with the speed of C/C++/Fortran~\cite{bezanson2017julia} while giving a convenient high-level programming environment. Julia is a built on top of the modularized LLVM compiler infrastructure~\cite{lattner2004llvm}, and features a Just-In-Time (JIT) compilation engine~\cite{aycock2003brief}. Therefore, Julia is ideal for agile development of advanced data science algorithms due to its speed and effectiveness in solving computationally complex problems. Also, Julia has support for parallelism and concurrency, which are crucial for HPC applications. In this paper, our major goal is to increase productivity by allowing data scientists to focus on writing high-level, performant numerical algorithms for legacy HPC applications at large-scale.

@@

We have run all our experiments on a cluster, Grizzly, located at Los Alamos National Laboratory (LANL). Grizzly consists of 1,490 compute nodes, and each node is equipped with two Intel Broadwell Xeon E5-2695v4 2.1GHz processors (18 cores per CPU) and 128GB 2400 MHz DDR4 memory.
The system runs on a Tri-Lab Operating System Stack (TOSS) and its nodes are connected by Intel OmniPath Host Fabric Interface (HFI) single port via PCIex16.
Grizzly uses Slurm for job scheduling and resource management. The total storage is 15PB.

\begin{table}
\centering 
  \caption{The E5-2695V4 CPU specifications}
  \label{table:layout}
  \begin{tabular}{lc}
 \toprule
  Specifications & Values \\
 \midrule
 Total Cores  & 18 \\
 Total Threads  & 36\\
 Max Turbo Frequency   & 3.30 GHz\\
 Processor Base Frequency & 2.10 GHz\\
 Cache   & 45 MB\\
 Memory Types  & DDR4\\
 Max Memory Bandwidth & 76.8 GB/s\\
 \bottomrule
\end{tabular}
\end{table}

>>>>

Julia is a dynamically-typed programming language that is for general-purpose application development and provides many Python-like features (e.g., rich package support)~\cite{bezanson2017julia}. The first public Julia release was introduced in 2013 and it is designed to provide users with the speed of C/C++/Fortran~\cite{bezanson2017julia} while giving a convenient high-level programming environment. Julia is a built on top of the modularized LLVM compiler infrastructure~\cite{lattner2004llvm}, and features a Just-In-Time (JIT) compilation engine~\cite{aycock2003brief}. Therefore, Julia is ideal for agile development of advanced data science algorithms due to its speed and effectiveness in solving computationally complex problems. Also, Julia has support for parallelism and concurrency, which are crucial for HPC applications. In this paper, our major goal is to increase productivity by allowing data scientists to focus on writing high-level, performant numerical algorithms for legacy HPC applications at large-scale.

@@

We have run all our experiments on a cluster, Grizzly, located at Los Alamos National Laboratory (LANL). Grizzly consists of 1,490 compute nodes, and each node is equipped with two Intel Broadwell Xeon E5-2695v4 2.1GHz processors (18 cores per CPU) and 128GB 2400 MHz DDR4 memory. Table~\ref{table:cpuspecs} shows the Xeon E5-2695v4 specifications. The system runs on a Tri-Lab Operating System Stack (TOSS) and its nodes are connected by Intel OmniPath Host Fabric Interface (HFI) single port via PCIex16.
Grizzly uses Slurm for job scheduling and resource management. The total storage is 15PB.

\begin{table}
\centering 
  \caption{The E5-2695V4 CPU specifications}
  \label{table:cpuspecs}
  \begin{tabular}{lc}
 \toprule
  Specifications & Values \\
 \midrule
 Total Cores  & 18 \\
 Total Threads  & 36\\
 Max Turbo Frequency   & 3.30 GHz\\
 Processor Base Frequency & 2.10 GHz\\
 Cache   & 45 MB\\
 Memory Types  & DDR4\\
 Max Memory Bandwidth & 76.8 GB/s\\
 \bottomrule
\end{tabular}
\end{table}
